Comparing vector-based and ACT-R memory models using large-scale datasets:\protect\\User-customized hashtag and tag prediction on Twitter and StackOverflow

### 2014-11-19 writeups/dissertation/dissertation.tex
foo

\title{Comparing vector-based and ACT-R memory models using large-scale datasets:\protect\\User-customized hashtag and tag prediction on Twitter and StackOverflow}
\shorttitle{Comparing memory models of tag retrieval}
%\shorttitle{}

@@

\def\committee{
  Michael D. Byrne, Chair \\
  Professor, Psychology and Computer Science \and
  Phillip Kortum \\
  Assistant Professor, Psychology \and
  David Lane \\
  Associate Professor, Psychology, Statistics, and Management \and
  Devika Subramanian \\
  Professor, Computer Science and Electrical Engineering \\
}

% Replace the title page in the apa6 style sheet with the title page from the Rice template
% The title page style was taken from Rice University LaTeX PhD template: http://scholarship.rice.edu/handle/1911/21747
% The following code for the abstract page was taken from the apa6 \maketitle command.
\makeatletter
\def\makeDisCover{
  \def\maketitle{
    \begin{titlepage}
      \singlespacing
      \null
      \vfill
      \vbox to 0pt{\vss\vbox to 8.75in{\parskip 0pt \parindent 0pt\centering
	{\uppercase\expandafter{Rice University} \par} \vskip 0pt plus 3fil
	{\bf \@title \par} \vskip 0pt plus 1.3fil
	{by \par} \vskip 0pt plus 1fil
	{\bf \@author \par} \vskip 0pt plus 3fil
	{\sc A Thesis Submitted \\
	  in Partial Fulfillment of the \\
	Requirements for the Degree \par} \vskip 0pt plus 1.1fil
	{\bf Doctor of Philosophy \par} \vskip 0pt plus 4.5fil
	\begingroup
	\leftskip .45\textwidth \rightskip 0pt plus 1fil
	{\sc Approved, Thesis Committee: \par} \vskip 2.5em
	\moveright\leftskip\vbox{\hrule width \leftskip}
	\def\and{\par \vskip 2.25em minus 1em\moveright\leftskip\vbox{\hrule width \leftskip}}
	\committee
	\par \endgroup
	\vskip 0pt plus 2fil
	{Houston, TEXAS \par} \vskip 0pt 
	{\monthnameenglish{} \number\year \par}
      }}
      \doublespacing
      \newpage
  %BDB\hyphenpenalty 10000
      \fussy
      \@ifundefined{@abstract}{}{%
	\section{\normalfont\normalsize\abstractname}% BDB
	\noindent\@abstract\par% BDB
	\@ifundefined{@keywords}{}{%
	  \setlength{\parindent}{0.4in}% BDB
	  \indent\textit{\keywordname:} \@keywords%
	}%
	\newpage
      }
      \@ifundefined{def@donotrepeattitle}{
	\section{\protect\normalfont{\@title}}
      }{}%
      \raggedright%
      \setlength{\parindent}{0.4in}%
    \end{titlepage}}
  }
\makeatother

%\makeDisCover

@@

@@

\section{Acknowledgements}

@@

\tableofcontents
\newpage

\listoftables
\newpage

\listoffigures
\newpage

>>>>

\title{Comparing vector-based and ACT-R memory models using large-scale datasets:\protect\\User-customized hashtag and tag prediction on Twitter and StackOverflow}
%\shorttitle{Comparing memory models of tag retrieval}
\shorttitle{}

@@

\def\committee{
  Michael D. Byrne, Chair \\
  Professor, Psychology and Computer Science \and
  Phillip Kortum \\
  Assistant Professor, Psychology \and
  Devika Subramanian \\
  Professor, Computer Science and Electrical Engineering \\
}

% Replace the title page in the apa6 style sheet with the title page from the Rice template
% The title page style was taken from Rice University LaTeX PhD template: http://scholarship.rice.edu/handle/1911/21747
% The following code for the abstract page was taken from the apa6 \maketitle command.
\makeatletter
\def\makeDisCover{
  \def\maketitle{
    \begin{titlepage}
      \singlespacing
      \null
      \vfill
      \vbox to 0pt{\vss\vbox to 8.75in{\parskip 0pt \parindent 0pt\centering
	{\uppercase\expandafter{Rice University} \par} \vskip 0pt plus 3fil
	{\bf \@title \par} \vskip 0pt plus 1.3fil
	{by \par} \vskip 0pt plus 1fil
	{\bf \@author \par} \vskip 0pt plus 3fil
	{\sc A Thesis Submitted \\
	  in Partial Fulfillment of the \\
	Requirements for the Degree \par} \vskip 0pt plus 1.1fil
	{\bf Doctor of Philosophy \par} \vskip 0pt plus 4.5fil
	\begingroup
	\leftskip .45\textwidth \rightskip 0pt plus 1fil
	{\sc Approved, Thesis Committee: \par} \vskip 2.5em
	\moveright\leftskip\vbox{\hrule width \leftskip}
	\def\and{\par \vskip 2.25em minus 1em\moveright\leftskip\vbox{\hrule width \leftskip}}
	\committee
	\par \endgroup
	\vskip 0pt plus 2fil
	{Houston, TEXAS \par} \vskip 0pt 
	{December \number\year \par}
      }}
      \doublespacing
      \newpage
  %BDB\hyphenpenalty 10000
      \fussy
      \@ifundefined{@abstract}{}{%
	\thispagestyle{empty}
	\section{\normalfont\normalsize \abstractname}% BDB
	\begingroup
	\parskip \z@ \parindent \z@ \par
	\null \vskip .1in \centering
	\@title
	\vskip .3in
	{by \par}
	\@author \par
	\vskip .5in
      \endgroup
      \@abstract\par% BDB
      \@ifundefined{@keywords}{}{%
	\setlength{\parindent}{0.4in}% BDB
	\indent\textit{\keywordname:} \@keywords%
      }%
      \thispagestyle{empty}
      \newpage
    }
    \@ifundefined{def@donotrepeattitle}{
      \section{\protect\normalfont{\@title}}
    }{}%
    \raggedright%
  \end{titlepage}
  \setlength{\parindent}{0.4in}%
}}
\makeatother

\makeDisCover

@@

\pagenumbering{roman}

@@

\thispagestyle{empty}
\section{Acknowledgements}

@@

\thispagestyle{empty}
\tableofcontents
\newpage

\thispagestyle{empty}
\listoftables
\newpage

\thispagestyle{empty}
\listoffigures
\newpage

\pagenumbering{arabic}
